Visual Exploration of Climate Data, Using Icon-Annotated Maps

### 2011-08-18 paper.tex
references

# Drawing trend lines on map
#   - How to
#   - Comparison to coloring slope
#   - Reference to Grinstein icon plots
#   - Alexander Gribov's work

>>>>

# Drawing trend lines on map
#   - How to
#   - Comparison to coloring slope
#   - Reference to Grinstein icon plots
# Pickett RM and Grinstein GG (1988). Iconographics 
# displays for visualizing multidimensional data. 
# In Proc. IEEE Conference on Systems, Man, and Cybernetics, pages 514-19.
# Note the later work on metaphoric data display, garbage work!
#   - Alexander Gribov's work http://rosuda.org/software/Gauguin/gauguin.html
